---
title: "Titanic DataSet Analysis Exploratory Analysis Part 2"
output:
  html_document:
    always_allow_html: yes
    df_print: paged
  pdf_document: default
  word_document: default
---
. Titanic dataset contains 891 rows and 12 columns.\n

. DataSet is downloaded from kaggle \n

. Notebook contains the indepth analysis of dataset including Probability,      Descriptive and Inferential Statistics.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)  
```

<b>Importing Libraries</b>
```{r}
library(dplyr)
library(ggplot2)
library(plotly)
library(ggthemes)
library(tidyr)
library(sqldf)

```

<b>Loading and viewing the structure of data</b>
```{r}
titanic <- read.csv("C:/Users/Hp/Desktop/titanic.csv",sep = ",",stringsAsFactors = TRUE,na.strings = NA,header = T)

str(titanic)
dim(titanic)
summary(titanic)
```

<b>Cleaning and changing the schema of data</b>
```{r}

# Removing the NULL values 
titanic<- na.omit(titanic)
dim(titanic)

#We can use sapply function to get the nº of missing values in our dataset
sapply(titanic,function(x) sum(is.na(x)))

# Converting to Factors

titanic$Pclass <- as.factor(titanic$Pclass)
titanic$Survived <- as.factor(titanic$Survived)
titanic$Sex <- as.factor(titanic$Sex)
titanic$Embarked <- as.factor(titanic$Embarked)

titanic$Survived<-ifelse(titanic$Survived==0,"Not Survivied","Survived")

titanic$Embarked<- ifelse(titanic$Embarked=="C","Cherbourg",(ifelse(titanic$Embarked=="Q","Queenstown","vSouthampton")))

```
<br>

<b> Adding a calulated Field</b>

```{r}
# Adding a calculated field column to dataset
titanic = titanic%>%
  mutate(family_size = SibSp + Parch)
```



```{r}
#Adding a Age category variable to dataset

age_categories <- cut(titanic$Age,breaks = c(0,20,50,80),labels = c("Children","Adults","OldAged"))

table(age_categories)

titanic$age_category<- age_categories


titanic<- na.omit(titanic)
```

<br>
<b>############    Using Probability it DataSet to find Insights   ############</b>


```{r}
# Probability of Survival 
ab<-table(titanic$Sex,titanic$Survived)
ab

#P(Survival) <- P(Survival|Female)*P(Female) + P(Survival|Male)*P(Male)
Prob_Survival<- 197/261 * 261/714 + 93/453 * 453/714
Prob_Survival

###-> 0.40 i.e 40% chances of Survival 


# Prob of Pclass 1 2 3
b<-table(titanic$Sex,titanic$Pclass)

#P(Pclass1)<- P(1|Female)*P(Female) + P(1|Male)*P(Male)
Prob_Pclass1 <- 85/261 * 261/714 + 101/453 * 453/714
Prob_Pclass1

###-> 0.26% i.e 26% People are from Pclass 1


#P(Pclass2)<- P(2|Female)*P(Female) + P(2|Male)*P(Male)
Prob_Pclass2 <- 74/261 * 261/714 + 99/453 * 453/714
Prob_Pclass2

###-> 0.24% i.e 24% People are from Pclass 2


#P(Pclass3)<- P(3|Female)*P(Female) + P(3|Male)*P(Male)
Prob_Pclass3<- 102/261 * 261/714 + 253/453 * 453/714
Prob_Pclass3

###-> 0.50% i.e 50% People are from Pclass 3 


#Prob of total is 1 
Prob_Pclass1 + Prob_Pclass2 + Prob_Pclass3


# Prob of children, adult and oldage
table(titanic$Sex,titanic$age_category)

#P(Children)<- P(children|Female)*P(Female) + P(Children|Male)*P(Male)
Prob_Children<- 77/261 * 261/714 + 102/453 * 453/714
Prob_Children

###-> .25 i.e 25% of Children are there


#P(Adults)<- P(Adults|Female)*P(Female) + P(Adults|Male)*P(Male)
Prob_Adults<- 167/261 * 261/714 + 304/453 * 453/714
Prob_Adults

###-> -.66 i.e 66% of Adults are there


#P(OldAge)<- P(Oldaged|Female)*P(Female) + P(Oldaged|Male)*P(Male)
Prob_OldAge<- 17/261 * 261/714 + 47/453 * 453/714
Prob_OldAge

###-> -.09 i.e 9% of OldAge are there


# Prob of family size 0,1,2,3,4,5
#table(titanic$Sex,titanic$family_size)

#P(FamilySize_0)<- P(0|Female)*P(Female) + P(0|Male)*P(Male)
Prob_FamilySize_0<- 100/261 * 261/714 + 304/453 * 453/714
Prob_FamilySize_0

###-> .56 i.e 56% of people were traveled alone


#P(FamilySize_1)<- P(1|Female)*P(Female) + P(1|Male)*P(Male)
Prob_FamilySize_1<- 72/261 * 261/714 + 67/453 * 453/714
Prob_FamilySize_1

###-> .19 i.e 19% of people travel with 1 person


#P(FamilySize_2)<- P(2|Female)*P(Female) + P(2|Male)*P(Male)
Prob_FamilySize_2<- 44/261 * 261/714 + 49/453 * 453/714
Prob_FamilySize_2

###-> .13 i.e 13% of people travel with 2 persons


#P(FamilySize_3)<- P(3|Female)*P(Female) + P(3|Male)*P(Male)
Prob_FamilySize_3<- 18/261 * 261/714 + 9/453 * 453/714
Prob_FamilySize_3

###-> .03 i.e 3% of people travel with 3 person.


# Prob of People from Cher,Queeen,vSouth
table(titanic$Sex,titanic$Embarked)

#P(Cherbourg)<- P(Cherbourg|Female)*P(Female) + P(Cherbourg|Male)*P(Male)
Prob_Cherbourg<- 61/261 * 261/714 + 69/453 * 453/714
Prob_Cherbourg

###->.18 i.e 18% of people boarded ship from Cherbourg


#P(Queenstown)<- P(Queenstown|Female)*P(Female) + P(Queenstown|Male)*P(Male)
Prob_Queenstown<- 12/261 * 261/714 + 16/453 * 453/714
Prob_Queenstown

###-> .04 i.e 4% of people boarded ship from Queenstown


#P(vSouthampton)<- P(vSouthampton|Female)*P(Female) + P(vSouthampton|Male)*P(Male)
Prob_vSouthampton<- 188/261 * 261/714 + 367/453 * 453/714
Prob_vSouthampton

###-> .78 i.e 78% of people boarded ship from vSouthampton
```

<br>

<b>############   Using Descriptive Statistics it DataSet to find Insights   ############</b>

<br>

<b><i>Comparing mean median mode of 2 numeric variables</i></b>
```{r}
twoVar<-titanic[c("Age","Fare")]

getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}



#Calculating Central Tendency of Age

mean(twoVar$Age)    
median(twoVar$Age)     
getmode(twoVar$Age)

mean(twoVar$Fare)    
median(twoVar$Fare)    
getmode(twoVar$Fare)
```
<br>


<b><i>We can see in both the variable mean is greater than median that means Skweness is towords Right.</i></b>


<b>Calculating Skewness (Mean>Median Right Skewed +ve), (Mean=Median=Mode Zero Skew,Symmetrical),(Mean<Median Left Skew -ve)</b>

<br>
<b>Cal mean and variance of fare</b>

```{r}
summary(twoVar$Age)

boxplot(twoVar$Age,col=twoVar$Age)

var(twoVar$Age)

#-> We can see the variance is too large to compare the dispersion of age, we have to use standard deviation

#Cal standard deviation and coff of variation (sd/mean) of age
sd(twoVar$Age)

#To Compare 2 variable we need coff of variance

coffOfVariation_age<- sd(twoVar$Age)/mean(twoVar$Age)
coffOfVariation_age

```
<br>

<b><i>1) We can see the coff of variation is .49

2) We can see the coff of variation is moderate so there is normal variation of age.

3)The higher the coefficient of variation, the greater the level of dispersion around the mean, as u can see from the boxplot. </i></b>


<br>
<b>Calculate variance of Fare</b>

```{r}
summary(twoVar$Fare)

boxplot(twoVar$Fare,col=twoVar$Fare)

var(twoVar$Fare)

#-> We can see the variance is too large to compare the dispersion of age, we have to use standard deviation

#Cal standard deviation and coff of variation (sd/mean) of age
sd(twoVar$Fare)

```

<b>To Compare 2 variable we need coff of variance</b>

```{r}
coffOfVariation_Fare<- sd(twoVar$Fare)/mean(twoVar$Fare)
coffOfVariation_Fare
```

<br>
<b><i>1) We can see the coff of variation is preety high so there is very high variation of fare.

2)I states that there may be possiblility of discrimination of fare.

3)The higher the coefficient of variation, the greater the level of dispersion around the mean, as u can see from the boxplot. </i></b>


<br>
<b>calculate covariance and correlation coefficient between age and fare</b>

```{r}
cov(twoVar$Age,twoVar$Fare)

#cal corelation coeff (corelation adjust covariance, so that relationship b/w 2 variables become easy to understand)

#(corelation coeff = cov(x,y)/sd(x).sd(y), -1 to 1 range)

sdMul<-sd(twoVar$Age)*sd(twoVar$Fare)

corelation_coeff_Age_Fare <-cov(twoVar$Age,twoVar$Fare)/sdMul
corelation_coeff_Age_Fare

```


<b><i> corr coff is .10 .We can conclude that there is pretty low correlation between age and fare.</i></b>


<br>
<b>Calculate covariance and correlation coefficient between fare and familysize</b>

```{r}
AgeFamilySize<-titanic[c("Fare","family_size")]

cov(AgeFamilySize$Fare,AgeFamilySize$family_size)

# cal corelation coeff (corelation adjust covariance, so that relationship b/w 2 variables become easy to understand)

#(corelation coeff = cov(x,y)/sd(x).sd(y), -1 to 1 range)

corelation_coeff_Fare_FamilySize<- cov(AgeFamilySize$Fare,AgeFamilySize$family_size)/sd(AgeFamilySize$Fare)*sd(AgeFamilySize$family_size)

corelation_coeff_Fare_FamilySize

```
<br>


<b><i>As the corelation_coeff is .45 i.e moderate +ve corelation. We can conclude that if Family Size increases the Fare increases.</i></b>


<br>
<b>Compare  fare distribution of 3 embarked </b>

```{r}
table(titanic$Embarked)

fare_prices1 <- sqldf("select fare from titanic where Embarked=='Cherbourg' limit 28")
fare_prices2 <- sqldf("select fare from titanic where Embarked=='Queenstown'")
fare_prices3 <- sqldf("select fare from titanic where Embarked=='vSouthampton' limit 28")

Fare_Distibution_of_Embarked<-cbind(fare_prices1,fare_prices2,fare_prices3)

colnames(Fare_Distibution_of_Embarked)<-c("Cherbourg","Queenstown","vSouthampton")

```

<b>Step1) Finding Mean Median and Mode of all 3 Embarked and comparing </b>

```{r}
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

 ##Cherbourg
mean(Fare_Distibution_of_Embarked$Cherbourg)  
median(Fare_Distibution_of_Embarked$Cherbourg)
getmode(Fare_Distibution_of_Embarked$Cherbourg)
 
 ##Queenstown
mean(Fare_Distibution_of_Embarked$Queenstown)
median(Fare_Distibution_of_Embarked$Queenstown)
getmode(Fare_Distibution_of_Embarked$Queenstown)

 ##vSouthampton
mean(Fare_Distibution_of_Embarked$vSouthampton)
median(Fare_Distibution_of_Embarked$vSouthampton)
getmode(Fare_Distibution_of_Embarked$vSouthampton)

```
<br>

<b>Step2) Finding Skewness
       ##-> All 3 are right skewed as Mean> Median  </b>

```{r}

g52<- ggplot(Fare_Distibution_of_Embarked) +
  theme_economist()+
  geom_density(aes(Cherbourg),col=c("brown"))+
  geom_vline(xintercept =mean(Fare_Distibution_of_Embarked$Cherbourg),col="green") +
  geom_vline(xintercept = median(Fare_Distibution_of_Embarked$Cherbourg),col="red")+
  geom_vline(xintercept = getmode(Fare_Distibution_of_Embarked$Cherbourg),col="blue") +
  labs(title = "Skeness of Mean(green), Median(red), Mode(blue)")

ggplotly(g52)

```
<br>

<b>Step3) Comparing variance, Sd and coff of variation of 3 </b>

```{r}
var(Fare_Distibution_of_Embarked$Cherbourg)
var(Fare_Distibution_of_Embarked$Queenstown)
var(Fare_Distibution_of_Embarked$vSouthampton)

```

<b>-> Since var is has a square unit we cant compare so we calculate sd.</b>

```{r}
sd(Fare_Distibution_of_Embarked$Cherbourg)
sd(Fare_Distibution_of_Embarked$Queenstown)
sd(Fare_Distibution_of_Embarked$vSouthampton)
```

<b>-> We need to cal coff of variation of comparision b/w the Embarked.</b>

```{r}
coff_Cher <- sd(Fare_Distibution_of_Embarked$Cherbourg)/mean(Fare_Distibution_of_Embarked$Cherbourg)
coff_Cher

coff_Queen <- sd(Fare_Distibution_of_Embarked$Queenstown)/mean(Fare_Distibution_of_Embarked$Queenstown)
coff_Queen

coff_vSouth <- sd(Fare_Distibution_of_Embarked$vSouthampton)/mean(Fare_Distibution_of_Embarked$vSouthampton)
coff_vSouth 
```
<br>

<b><i> We can see that all 3 have coff of variation >1 i.e they are highly correlated.So we can conclude their fare variablity is highly distributed around the mean specially vSouthampton. </i></b>


<br>
<b>############   Using Inferential Statistics it DataSet to find Insights   ############</b>

<br>
<b>Calculating Confidence Interval of Ages for 95% confidence</b>

```{r}
#taking sample of 121 
ages<- titanic["Age"]

ages2<- ages[200:321,]

### As the population variance is unknown we will use Student's T distribution

### We are using 95% confidence level

#Step1) Calculating mean, sd and SE
mean(ages2)
sd(ages2)
SE <- sd(ages2)/sqrt(121)
SE

#Step2) Finding T statistic 
# Degree of Freedom = n-1 = 121-1 = 120 and for 95% confidence i.e alpha is 5% so alpha/2 is .25
qt(.95,120)
t_statisic <- 1.65   #from T statistic table

#using the formula to find confidence interval 

#### [mean(ages2) - 1.65*SE , mean(ages2) + 1.65*SE]

29.68852 - 1.65*1.237137

29.68852 + 1.65*1.237137

#### [27.64,31.72]

#### We are 95% confident that the mean of Ages of polulation will be between [27.64,31.72]

```
<br>

<b>Calculating Confidence Interval of Fare for 95%, 99% confidence</b>

```{r}
#taking sample of 121
fares<- titanic$Fare
fares<- fares[400:521]

#Step1) Calculating mean, sd and SE
mean(fares)
sd(fares)
SE <- sd(fares)/sqrt(121)
SE

#Step2) Finding T statistic 
# Degree if Freedom = n-1 = 121-1 = 120 and for 95% confidence i.e alpha is 5% so alpha/2 is .25

qt(.95,120)  # T statistic for 95% confidence
qt(.99,120)  # T statistic for 99% confidence

t_statisic <- 1.65 

t_statisic2 <- 2.35 

#using the formula to find confidence interval 

# For 95% condidence
#### [mean(fares) - t_statisic*SE , mean(fares) + t_statisic*SE]
32.07995 - 1.65*2.726885
32.07995 + 1.65*2.726885

#### [27.58,36.58]

```

<b><i> We are 95% confident that the mean of Fare of polulation will be between [27.58,36.58] </i></b>

```{r}
# For 99% condidence
#### [mean(fares) - t_statisic2*SE , mean(fares) + t_statisic*SE]
32.07995 - 2.35*2.726885
32.07995 + 2.35*2.726885

#### [25.67,38.49]
```

<b><i>We are 99% confident that the mean of Fare of polulation will be between [25.67,38.49] </i></b>

<br>

<b>Calculating Confidence Interval of Fare wrt Queenstown and vSouthampton for Pclass 3 </b>

```{r}
#### Independent Samples but variance assumed to be equal 

fare_prices4 <- sqldf("select fare from titanic where Embarked=='Queenstown' and Pclass=3")
fare_prices5 <- sqldf("select fare from titanic where Embarked=='vSouthampton' and Pclass=3 limit 24")

Fare_Compare<-cbind(fare_prices4,fare_prices5)
colnames(Fare_Compare)<-c("Queenstown","vSouthampton")

```

```{r}
#1)Cal mean and sd
mean(Fare_Compare$Queenstown)      
mean(Fare_Compare$vSouthampton)

sd(Fare_Compare$Queenstown)
sd(Fare_Compare$vSouthampton)

nrow(Fare_Compare)

#Step2) Calculate unbiased estimator i.e pooled sample variance
pooled_variance <- 23*8.84^2 + 23*12.75^2 /46
polled_variance<-120.354
polled_sd<- sqrt(120.354)
polled_sd

# Step3) Calculating Student's T statistic

#Degree of freedom is 24 +24 -2 =46 and confidence level is 95%
qt(.95,46)

t_statisic_fare <- 1.67

#appling formula
(18.20972 - 12.7809) - 1.67*sqrt(120.354/24 + 120.354/24)

(18.20972 - 12.7809) + 1.67*sqrt(120.354/24 + 120.354/24)

#### [0.14,10.72]

```
<br>

<b><i> We are 95% confident that we can say that the one Embared has greater Fare for Pclass 3 than another by a margin of interval between [0.14,10.72] </i></b>


<br>
<b>Standardizing the Normal Distribution for age</b>

<i>As the sample size increases the distribution becomes standard normal distribution.

We will take small Sample and Standardize it </i>

```{r}
#taking sample of 121 
ages<- titanic["Age"]
ages2<- ages[200:321,]

head(ages2)

ages2 <- as.data.frame(ages2)
colnames(ages2)<-c("Age")
```

```{r}
hist(ages2$Age,col=rainbow(7),main="Histogram of Age Distribution")

mean(ages2$Age)   
sd(ages2$Age) 
```

```{r}
#-> Finding Standard Error  sd/sqrt(n)
standard_error <- sd(ages2$Age)/sqrt(nrow(ages2))
standard_error

```
<br>

<b><i>1) We can see the Standard Error 1.23

2) As the sample size increases Standard Error decreases.

3)mean 29.68 and sd =13.6 so i.e Right Skewed</i></b>


-> We have to standardize the distribution

```{r}
#-> We have to find Z score i.e x-mean /sd 

#1)Step x- mean
sub_mean<-ages$Age - mean(ages$Age)

mean(sub_mean)
sd(sub_mean)
hist(sub_mean,col=rainbow(7))

```

<b><i>We can see that the mean is almost 0 and sd is same as before 14.52 and graph has shifted to 0.</i></b>

```{r}
#Step 2) 
#-> Dividing the sub_mean by standard devaiation (sd)
z_score <- sub_mean/sd(sub_mean)

mean(z_score)

sd(z_score)

```

<b><i> We can see that the mean is approximately 0 sd=1 i.e standard normal distribution </i></b>

```{r}
z_df <- as.data.frame(z_score)  

ggplot(z_df) +
  geom_density(aes(z_df$z_score))

#-> Finding Standard Error  sd/sqrt(n)
standard_error2 <- sd(z_df$z_score)/sqrt(nrow(z_df))
standard_error2

```

<b><i>1)We can see the Standard Error as 0.037. After performing Standard normal distribution which is good.</i></b>

After performing Standard normal distribution we have reduced Standard Error from 1.23 we have reduced to 0.037 which is good. </i></b>


<br>
<b> ############   Hypothesis Testing   ############  </b>
<br>

<b>Find if the mean of Age is less than 30 or not.</b>
```{r}
#Test at 5% significance. Calculate the p-value of the test

#Taking sample of 121 ages
ages<- titanic["Age"]
ages2<- ages[200:321,]

# Step1) Writing null and alternative hypothesis 

# H0:mean of age is<=30
# H1:mean of age is>30


# Its a one-sided tail test

# Step2) Cal the mean,sd and SE
mean(ages2)
sd(ages2)
SE <- sd(ages2)/sqrt(121)
SE

# Step3) Finding T Score
# T= x- hyphosis_mean(x) / SE

# T = 29.688652 - 30 / SE

# T= -0.25   [we will take 0.25 as its easier to work with +ve and compare absolute values]

# Finding Critical T value and comapring
# as degree of freedom is 120 and we are caluclation at alpha=0.05 (95%)
qt(.95,120)
# t = 1.658

#0.25 < 1.658 i.e  T< t

#### As per decision rule if absoulte value of T score < critical T, we Accept Null Hyphothesis

#### So,We accept the null Hyphothesis test

#### So, at this level of significance we can 't say if the mean is >30

# T test for 95% confidence interval
t.test(ages2,mu=30,alternative = "greater",conf.level = 0.95)

# Step4) Finding P value
pt(0.25,120,lower.tail = FALSE)

```
<br>


<b><i>The p-value is .401507. 

1) 0.40 > 0.05 i.e P > alpha so as per decision rule we accept the null hyphothsis.

2) So at 5% significance level we can't say that the mean is >30

3) The result is Not Significant


-> If we test at 1% significat level

1) 0.40 > 0.01 i.e P > alpha therefore, we cannot reject the null hypothesis.

2) So at 1% significance level we can't say that the mean is >30.

3) The result is Not Significant.  
</i></b>


<br>
<b>Find if the average Fare is less than 30</b>

```{r}
#Test at 5% and 1% significance. Calculate the p-value of the test

#Taking sample of 121 ages
fares2<- titanic$Fare[200:321]

# Step1) Writing null and alternative hypothesis 

# H0:mean of age is<=30
# H1:mean of age is>30

# Its a one-sided tail test

# Step2) Cal the mean,sd and SE

fares2<- titanic$Fare[200:321]

head(fares2)

mean(fares2)

sd(fares2)
SE <- sd(fares2)/sqrt(121)
SE

# Step3) Finding T Score
# T= x- hyphosis_mean(x) / SE

# T = 48.72579 - 30 / SE

# T= 2.85   

# Finding Critical T value and comapring
# as degree of freedom is 120 and we are caluclation at alpha=0.05 (95%)
qt(.95,120)

# t = 1.658

# 2.85 > 1.658 i.e  T> t

#### As per decision rule if absoulte value of T score > critical T, we reject Null Hyphothesis

#### We accept the Alternate Hyphothesis test

#### So, at this level of significance we can say that average fare is >30



# T test for 95% confidence interval
t.test(fares2,mu=30,alternative = "greater",conf.level = .95)



# Step4) Finding P value

pt(2.85,120,lower.tail = FALSE)
```

<br>
<b><i>
The p-value is .002

1) .002 < 0.05 i.e P < alpha so as per decision rule we reject the null hyphothsis.

2) So at 5% significance level we can say that the average fare is >30

3) The result is Significant.


-> If we test at 1% significat level

1) .002 < 0.01 i.e P < alpha therefore, we reject the null hypothesis.

2) So at 1% significance level we can say that average fare is >30.

3) The result is Significant.    
</i></b>


<br>
<b> See if Fare in Queenstown and Fares in vSouthampton wrt Pclass 3 are same</b>

```{r}
#### Independent Samples but variance assumed to be equal

#Test at 5% and 1% significance. Calculate the p-value of the test

fare_prices4 <- sqldf("select fare from titanic where Embarked=='Queenstown' and Pclass=3")
fare_prices5 <- sqldf("select fare from titanic where Embarked=='vSouthampton' and Pclass=3 limit 24")

Fare_Compare<-cbind(fare_prices4,fare_prices5)
colnames(Fare_Compare)<-c("Queenstown","vSouthampton")


head(Fare_Compare)
```


```{r}
#Taking sample of 121 ages

# Step1) Writing null and alternative hypothesis 

# H0: mean(Q) = mean(V)  i.e mean(Q) - mean(V) = 0
# H1: mean(Q) != mean(V) i.e mean(Q) - mean(V) != 0


# Step2) Cal the mean,sd and SE

head(Fare_Compare)

m1<-mean(Fare_Compare$Queenstown)  
m1

m2<-mean(Fare_Compare$vSouthampton)
m2

sd(Fare_Compare$Queenstown)      
sd(Fare_Compare$vSouthampton)

#Calculating Standard Error
SE1 <- sd(Fare_Compare$vSouthampton)/sqrt(48)
SE2 <- sd(Fare_Compare$Queenstown)/sqrt(48)

SE<-SE1+SE2 # SE-> Standard Error
SE

nrow(Fare_Compare)


#Step3) Calculate unbiased estimator i.e pooled sample variance

#degree_freedom<- 24+24-2 
degree_freedom= 46

# using formula of Pooled variance -> (n1-1)*sd1^2 + (n2-1)*sd2^2 /(n1+n2-2) 
pooled_variance <- 23*8.84^2 + 23*12.75^2 /46  
polled_variance<-120.354
polled_sd<- sqrt(120.354)
polled_sd

# Step4) Finding T Score
#t_score <- diff of sample mean - diff of hyphothsis mean / SE

#t_score <- (m2 - m1) - 0 /SE
t_score <-5.428/SE
t_score


# Step5) Finding Critical T value and comapring

#Degree of freedom is 24 +24 -2 =46 and confidence level is 95%
qt(.95,46)

# 1.71 > 1.678 i.e  T> t

#### As per decision rule if absoulte value of T score > critical t, we reject Null Hyphothesis

#### We accept the Alternate Hyphothesis test'

#### The Result is Significant

####-> So, at 95% level of significance we can say that average fare of Queenstown and Fares in vSouthampton wrt Pclass 3 are NOT SAME

# Step4) Finding P value

pt(1.71,46,lower.tail = FALSE)
```
<br>

<b><i>
1) .047 < 0.05 i.e P < alpha so as per decision rule we reject the null hyphothsis.

2) So at 5% significance level we can say that the average fare of Queenstown and Fares in vSouthampton wrt Pclass 3 are not same

3) The result is Significant

-> If we test at 1% significat level

1) .047 > 0.01 i.e P > alpha i.e P > alpha so as per decision rule we accept the null hyphothsis

2) We see if we take at 1% significant level, We have to accept Null Hyphothsis i.e average fare of both are same.

3) The result won't be Significant

4) So upto .047 the result is significant after that result is not significant. 


5)Its upto statistician which value he want to take.  
</i></b>


<br>
<b>Check if there is fare discrimination based on gender </b>

```{r}
#### Independent sample unknown variance assumed to be equal

titanic_male<- titanic[titanic$Sex=="male",]
nrow(titanic_male)

titanic_female<- titanic[titanic$Sex=="female",]
nrow(titanic_female)

# Step1) Writing Null and Alternative Hyphothesis 

# H0: Mean_Fare_Male = Mean_fare_Female  i.e  mean(M) - mean(F) = 0
# H1: Mean_Fare_Male != Mean_fare_Female  i.e  mean(M) - mean(F) != 0

# Step2) Cal Mean, Sd of Sal wrt

m1<-mean(titanic_male$Fare)
m1

m2<-mean(titanic_female$Fare)
m2

sd(titanic_male$Fare)      
sd(titanic_female$Fare)

#Finding standard error

SE1<-sd(titanic_male$Fare)/sqrt(nrow(titanic_male))
SE2<-sd(titanic_female$Fare)/sqrt(nrow(titanic_female)) 
SE <- SE1 + SE2
SE

# Step3) Cal Pooled Sample variance

#degree_freedom<- 453+261-2 
degree_freedom = 712

# using formula of Pooled variance -> (n1-1)*sd1^2 + (n2-1)*sd2^2 /(n1+n2-2)
pooled_variance <- 452*45.84189^2 + 260*61.34685^2 /712
polled_variance<-2708.374
polled_sd<- sqrt(2708.374)
polled_sd

# Step4) Finding T score

# T_score <- (m2 - m1) - 0 /SE
T_score <-m2-m1
T_score <- T_score/SE
T_score

# Step5) Finding Critical t value and comapring

#Degree of freedom is 24 +24 -2 =46 and confidence level is 95%
qt(.95,712)

# 3.41 > 1.64 i.e  T> t

#### As per decision rule if absoulte value of T score > critical t, we reject Null Hyphothesis

#### We accept the Alternate Hyphothesis test'

#### The Result is Significant

####-> So, at  95% level of significance we can say thattheir is fare discrimination based on gender.


# Step 6) Cal P value

pt(3.4,712,lower.tail = FALSE)

```
<br>

<b><i>
The p-value is .000356  

1) At 5% significance level

2) .000356 < 0.05 i.e P < alpha #-> So as per deciction rule we reject the NULL hyphothesis

3) So at 5% significance level we can say that their is fare discrimination based on gender.

4) The result is Significant


-> If we test at 1% significat level

1) .000356 < 0.01 i.e P < alpha So as per deciction rule we reject the NULL hyphothesis


2) So at 1% significance level we can say that their is fare discrimination based on gender.


3) The result is Significant  </i></b>


<br>
  <b>We can go more indepth to see the fare discrimination </b>
<br>


<b>Check if there is fare discrimination based on gender above 35 and below 35</b>

```{r}
####Independent sample unknown variance assumed to be equal 

# Above 35
titanic_male_above35<- titanic[titanic$Age>35 & titanic$Sex=="male",]
nrow(titanic_male_above35)

titanic_female_above35<- titanic[titanic$Age>35 & titanic$Sex=="female",]
nrow(titanic_female_above35)

# Below 35
titanic_male_below35<- titanic[titanic$Age<35 & titanic$Sex=="male",]
nrow(titanic_male_below35)

titanic_female_below35<- titanic[titanic$Age<35 & titanic$Sex=="female",]
nrow(titanic_female_below35)

### Finding for Above Above 35

# Step1) Writing Null and Alternative Hyphothesis 

# H0: Mean_Fare_male_Above35 = Mean_fare_female_Above35  i.e  mean(M) - mean(F) = 0
# H1: Mean_Fare_male_Above35 != Mean_fare_female_Above35  i.e  mean(M) - mean(F) != 0

# Step2) Cal Mean, Sd of Sal wrt

m1<-mean(titanic_male_above35$Fare)    
m1

m2<-mean(titanic_female_above35$Fare)
m2

sd(titanic_male_above35$Fare)      
sd(titanic_female_above35$Fare)

#Calculating Standard Error

SE1 <- sd(titanic_male_above35$Fare)/sqrt(nrow(titanic_male_above35))
SE2 <- sd(titanic_female_above35$Fare)/sqrt(nrow(titanic_female_above35))
SE <- SE1 + SE2
SE  # Standard Error


# Step3) Cal Pooled Sample variance

#degree_freedom<- 144+73-2 
degree_freedom= 214

# using formula of Pooled variance -> (n1-1)*sd1^2 + (n2-1)*sd2^2 /(n1+n2-2)
pooled_variance <- 143*53.19955^2 + 72*57.84898^2 /215 
polled_variance<-3003.097
polled_variance
polled_sd<- sqrt(polled_variance)
polled_sd


# Step4) Finding T score
#T_score <- (m2 - m1) - 0 /SE
T_score =  (m2-m1)/SE 
T_score

```

->We can directly go for finding P value also instead of finding critical t value and comparing first

```{r}
# Step 5) Cal P value
pt(2.35,215,lower.tail = FALSE)

```
<br>

<b><i>
So the p value is 0.009

1) At 5% significance level

2) .009 < 0.05 i.e P < alpha 

3) So as per deciction rule we reject the NULL hyphothesis

4) So at 5% significance level we can say that their is fare discrimination based on gender of age above 35.


-> The result is Significant


1) If we test at 1% significat level

2) .009 < 0.01 i.e P < alpha 

3) So as per deciction rule we reject the NULL hyphothesis

4) So at 1% significance level we can say that their is fare discrimination based on gender of age above 35.


5) The result is Significant   </i></b>


<br>
<b>Finding for Age Below 35 </b>

```{r}
# Step1) Writing Null and Alternative Hyphothesis 

# H0: Mean_Fare_male_Below35 = Mean_fare_female_Below35  i.e  mean(M) - mean(F) = 0
# H1: Mean_Fare_male_Below35 != Mean_fare_female_Below35  i.e  mean(M) - mean(F) != 0

# Step2) Cal Mean, Sd of Sal wrt

m1<-mean(titanic_male_below35$Fare)    
m1

m2<-mean(titanic_female_below35$Fare)    
m2

sd(titanic_male_below35$Fare)
sd(titanic_female_below35$Fare)


#Calculating Standard Error

SE1 <- sd(titanic_male_below35$Fare)/sqrt(nrow(titanic_male_below35))
SE2 <- sd(titanic_female_below35$Fare)/sqrt(nrow(titanic_female_below35))
SE <- SE1 + SE2
SE  # Standard Error
```

```{r}
# Step3) Cal Pooled Sample variance

#degree_freedom<- 299+180-2 
degree_freedom= 477

# using formula of Pooled variance -> (n1-1)*sd1^2 + (n2-1)*sd2^2 /(n1+n2-2)
pooled_variance <- 299*31.26985^2 + 180*51.83092^2 /477
polled_variance<-1626.673
polled_variance
polled_sd<- sqrt(polled_variance)
polled_sd

# Step4) Finding T score
#T_score <- (m2 - m1) - 0 /SE
T_score <-  (m2-m1)
T_score <- T_score/SE
T_score
```

<b>
We can directly go for finding P value also instead of finding critical t value and comparing first.</b>

```{r}
# Step 5) Calculate P value
pt(2.89,477,lower.tail = FALSE)
```
<br>

<b><i>

The P value is 0.002

1) At 5% significance level

2) .002 < 0.05 i.e P < alpha 

3) So as per deciction rule we reject the NULL hyphothesis

4) So at 5% significance level we can say that their is fare discrimination based on gender of age below 35.

5) The result is Significant


-> If we test at 1% significat level

1) .002 < 0.01 i.e P < alpha 

2) So as per deciction rule we reject the NULL hyphothesis

3) So at 1% significance level we can say that their is fare discrimination based on gender of age below 35.


4) The result is Significant  </i></b>


<br>
<b>Comparing mean age of survived and non survived</b>

```{r}
class(titanic$Age)
class(titanic$Survived)

boxplot(titanic$Age~titanic$Survived,col=rainbow(2),main="BoxPlot of Survival vs Age")

#finding variance, sd and coff of variation 
var(titanic$Age[titanic$Survived=="Survived"])
var(titanic$Age[titanic$Survived=="Not Survivied"])

v1<-sd(titanic$Age[titanic$Survived=="Survived"])
v1

v2<-sd(titanic$Age[titanic$Survived=="Not Survivied"])
v2

v3<-mean(titanic$Age[titanic$Survived=="Survived"])
v3

v4<-mean(titanic$Age[titanic$Survived=="Not Survivied"])
v4

cov_age_survived<- v1/v3
cov_age_survived

cov_age_not_survived<- v2/v4
cov_age_not_survived


#H0: Mean age of survived = not survived   i.e  Mean age of survived
#H1: Mean age of survived != not survived

####non equal variance , 2 sided test, Independent groups i.e not paired.

t.test(titanic$Age~titanic$Survived,mu=0,alt="two.sided",conf=0.95,var.eq=F,paired=F)

```
<br>
<b><i>

1) As P value is 0.04 < .05 conf so we reject the null hyphothisis.


2) Mean age of survived and not survived are different.  </i></b>

```{r}
kruskal.test(titanic$Age~titanic$Survived)

#### Using Kruskal test also we can conclude Mean age of survived and not survived are different

```